---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dyadr
[![Travis-CI Build Status](https://api.travis-ci.org/abarylsky/dyadr.svg?branch=master)](https://travis-ci.org/abarylsky/dyadr)


r package for dyadic data analysis

# Description
An R package for assisting people in dyadic data analysis. Contains functions to organize output from the `gls` and `lme` functions from the `nlme` package for cross-sectional data. Some functionality exists with the `lme4` package. Improves user understanding of the Actor-Partner Independence Model by organizing actor and parter effects for the purpose of comparing parameters to each other. 

# Installation
```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("RandiLGarcia/dyadr")
```

# Usage

Here is an example of how to use some of the `dyadr` functions.

First, load the package and get data:
```{r, warning = FALSE}
library(nlme)
library(dyadr)
```

Using the `smallsummary` function

```{r}
apim <- gls(Satisfaction_A ~ Tension_A + SelfPos_P,
  na.action = na.omit,
  correlation = corCompSymm(form = ~ 1 | CoupleID),
  data = acipair
)

smallsummary(apim)
```

Using the `crsp` function

```{r}
# Empty Model
apimie <- summary(gls(Satisfaction_A ~ 1,
  na.action = na.omit,
  correlation = corCompSymm(form = ~ 1 | CoupleID),
  data = acipair
))
# sd of errors for the model or esd
esd <- as.numeric(apim[6])
# sd of errors for the empty model or esd0
esd0 <- as.numeric(apimie[6])
# the R squared, using the crsp function
crsp(esd, esd0)
```

# Contributing
Feel free to submit pull requests resolving documented issues. 

# Authors
* **Randi L. Garcia** - *Initial work* - [dyadr](https://github.com/RandiLGarcia/dyadr)
* **David A. Kenny** - *Initial work* 
